Predicting the 2024 US Presidential Election with a Model-Based Forecast

### 2024-10-28 paper/paper.qmd
update paper

\begin{align}
y_i \mid \mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \
\mu_i &= \beta_0 + \beta_1 \cdot numeric_grade_i + \beta_2 \cdot methodology_i + \beta_3 \cdot duration_i + \beta_4 \cdot sample_size_i + \beta_5 \cdot transparency_score_i + \beta_6 \cdot state_i + \epsilon_i \
\epsilon_i &\sim \text{Normal}(0, \sigma^2)
\end{align}

Where:
Where: 
\begin{align}
\beta_0 & \text{ is the intercept term} \\
\beta_1, \beta_2, \beta_3, \beta_4, \beta_5, \beta_6 & \text{ are the coefficients for each predictor} \\
\sigma^2 & \text{ is the variance of the error term}
\end{align}

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  )
)
```

>>>>

\begin{align*}
    y_i \mid \mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \\
    \mu_i &= \beta_0 + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{methodology}_i \\
          &\quad + \beta_3 \cdot \text{duration}_i + \beta_4 \cdot \text{sample\_size}_i \\
          &\quad + \beta_5 \cdot \text{transparency\_score}_i + \beta_6 \cdot \text{state}_i + \epsilon_i \\
    \epsilon_i &\sim \text{Normal}(0, \sigma^2)
\end{align*}

\textbf{Where:}
\begin{itemize}
    \item $\beta_0$ is the intercept term.
    \item $\beta_1, \beta_2, \beta_3, \beta_4, \beta_5, \beta_6$ are the coefficients for each predictor.
    \item $\sigma^2$ is the variance of the error term.
\end{itemize}

@@
